Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-07-20 docs/paper/paper.Rmd
more metadata detail

# Load forecast metedata. See data-raw/get-hub-metadata.R for munging
metadata <- fread(here("data", "metadata.R"))

@@

```{r metadata}
# Number of locations
locations <- metadata |>
  DT(, location) |>
  unique() |>
  length()

# Number of models overall
models <- metadata |>
  DT(, model) |>
  unique() |>
  length()

# Models per forecast date
models_per_forecast <- metadata |>
  summarise_forecasts_by(by = "forecast_date")

@@

@@

@@

# Partial coverage models
partial_coverage <- locations_per_model |>
  DT(n > 1) |>
  DT(n <= 30)

# Models coverage of forecast datees
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "forecast_date", by = "model") |>
  DT(order(n))
```

@@

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK). 
- Date range of forecasts
- Forecasts per country
- Total number of forecast models and average per location and per forecast date
- Summarises general trends in incidence in the data

>>>>

# Load forecast metedata. See data-raw/get-hub-metadata.R for munging
metadata <- fread(here("data", "metadata.csv"))

@@

```{r metadata}
# Number of locations
locations <- metadata |>
  DT(, uniqueN(location))

# Number of models overall
models <- metadata |>
  DT(, uniqueN(model))

# Number of forecast dates
forecast_dates <- metadata |>
  DT(, uniqueN(target_end_date))

# Forecasts

# Models per forecast date
models_per_forecast <- metadata |>
  summarise_forecasts_by(by = "target_end_date")

@@

locs_per_model_single_date <- metadata |>
    summarise_forecasts_by(
    var = "location", by = c("model", "target_end_date")
    ) |>
    DT(, unique(.SD[n == max(n), .(n)]), by = "model")

locs_per_model_date <- metadata |>
  summarise_forecasts_by(
    var = "location", by = c("model", "target_end_date")
  ) |>
  DT(locs_per_model_single_date[, .(model, max_n = n)], on = "model") |>
  DT(, n_per := n / max_n) |>
  DT(, .SD[!all(n == max_n)], by = "model")

models_per_loc_date <- metadata |>
  summarise_forecasts_by(var = "model", by = c("target_end_date", "location"))

@@

# Local models
local_models <- locations_per_model |>
  DT(n == 1) |>
  DT(, model)

@@

# Partial coverage models
partial_models <- locations_per_model |>
  DT(n > 1) |>
  DT(n <= 30)

# Models coverage of forecast datees
forecast_dates_by_models <- metadata |>
  summarise_forecasts_by(var = "target_end_date", by = "model") |>
  DT(order(n))
```

@@

We extracted forecasts starting from the 15th of January until the 19th of July 2022 for all countries covered by the ECDC forecasting hub (all ECDC nations and the UK making `r locations` unique locations). In total `r nrow(metadata)` forecasts were made across all locations, `r forecast_dates` forecast dates from `r models` independent forecast models (including the ECDC baseline model). Of these models, `r length(global_models)` forecasted in at least 30 locations including our original submission  (referred to as "epiforecasts-EpiNow2" by the hub), and our surrogate model (referred to as "epiforecasts-weeklygrowth" by the hub). Of the remainining models submitted `r length(local_models)` were submitted in only one location. These models were gernerally submitted to a subset of locations with particular clustering in Germany and Poland (likely due to the folding of the German/Poland forecasting hub into the ECDC forecasting hub project). Italy was also an outlier with `r single_locs_models_per_loc[location == "IT", n]` models that submitted nowhere else. `r length(partial_models)` models submitted for between 2 and 30 locations likely indicating manual curation of submissions.

Across all forecast dates and locations the minimum number of independent forecasts was `r models_per_loc_date[, min(n)]` with the maxmimum being `r models_per_loc_date[, max(n)]`. The median number of independent forecasts per location and forecast date was `r models_per_loc_date[, median(n)]`. Across all forecast dates all locations recieved forecasts from at least `r models_per_location[, min(n)]` models with the median number of forecast models per location being `r models_per_location[, median(n)]`.

- Date range of forecasts
- Forecasts per country
- Total number of forecast models and average per location and per forecast date
- Summarises general trends in incidence in the data
